\LARGE \bf Energy-Aware Dynamic Mission Planning Algorithm for UAVs

### 2020-11-16 icra-2021.tex
proofing

  @inproceedings{seewald2020beyond,
    title={Beyond Traditional Energy Planning: the Weight of Computations in Planetary Exploration}, 
    author={Seewald, Adam},
    booktitle={IROS Workshop on Planetary Exploration Robots: Challenges and Opportunities (PLANROBO20)},
    pages={3},
    year={2020},
    publisher={ETH Zurich, Department of Mechanical and Process Engineering},
    DOI={10.3929/ethz-b-000450120},
    url={https://adamseew.bitbucket.io/short/beyond2020}
  }
  @inproceedings{lindemann2005smoothly,
    title={Smoothly blending vector fields for global robot navigation},
    author={Lindemann, Stephen R and LaValle, Steven M},
    booktitle={Proceedings of the 44th IEEE Conference on Decision and Control},
    pages={3553--3559},
    year={2005},
    organization={IEEE}
  }
  @article{gonccalves2010vector,
    title={Vector fields for robot navigation along time-varying curves in $n$-dimensions},
    author={Gon{\c{c}}alves, Vin{\'\i}cius M and Pimenta, Luciano CA and Maia, Carlos A and Dutra, Bruno CO and Pereira, Guilherme AS},
    journal={IEEE Transactions on Robotics},
    volume={26},
    number={4},
    pages={647--659},
    year={2010},
    publisher={IEEE}
  }
  @inproceedings{panagou2014motion,
    title={Motion planning and collision avoidance using navigation vector fields},
    author={Panagou, Dimitra},
    booktitle={2014 IEEE International Conference on Robotics and Automation (ICRA)},
    pages={2513--2518},
    year={2014},
    organization={IEEE}
  }
  @inproceedings{zhou2014vector,
    title={Vector field following for quadrotors using differential flatness},
    author={Zhou, Dingjiang and Schwager, Mac},
    booktitle={2014 IEEE International Conference on Robotics and Automation (ICRA)},
    pages={6567--6572},
    year={2014},
    organization={IEEE}
  }
  @article{kapitanyuk2017guiding,
    title={A guiding vector-field algorithm for path-following control of nonholonomic mobile robots},
    author={Kapitanyuk, Yuri A and Proskurnikov, Anton V and Cao, Ming},
    journal={IEEE Transactions on Control Systems Technology},
    volume={26},
    number={4},
    pages={1372--1385},
    year={2017},
    publisher={IEEE}
  }
  @book{kuo1967automatic,
    title={Automatic Control Systems},
    author={Kuo, B.C.},
    isbn={9780130549730},
    lccn={67016388},
    series={Electrical engineering series},
    year={1967},
    publisher={Prentice-Hall}
  }
\end{filecontents}

@@

Consider a linear time-invariant (LTI) state-space model
\begin{equation}\label{eq:state-perf}\begin{split}
  \mathbf{q}_{k+1}&=A\mathbf{q}_{k}+B\mathbf{u}_{k}+\mathbf{w}_k,\\
  y_k&=C\mathbf{q}_k+v_k,
\end{split}\end{equation}
where $y_k\in\mathbb{R}_{\geq 0}$ is the instantaneous energy consumption. The state $\mathbf{q}$ are the energy coefficients
\begin{equation}\label{eq:state-details}\begin{split}
  \mathbf{q}_k&=\left[\begin{array}{cccccc}
    \alpha_0 & \alpha_1 & \beta_1 & \cdots & \alpha_r & \beta_r
  \end{array}\right]^T,\\
  A&=\left[\begin{array}{cccc}
    1&    &       &  \\
     & A_1&       &  \\
     &    & \ddots&  \\
     &    &       & A_r 
  \end{array}\right],\,A_i=\begin{bmatrix}0 & i/\xi \\ -i^2/\xi^2 & 0\end{bmatrix},\\
  C&=\left[\begin{array}{cccccc}
    1 & 1 & 0 & \cdots & 1 & 0
  \end{array}\right],
\end{split}\end{equation}
where $\mathbf{q}_k\in\mathbb{R}^m$ given $m=2r+1$, $A\in\mathbb{R}^{m\times m}$ is the state transmission matrix, and $C\in\mathbb{R}^m$ is the output matrix. In matrix $A$, the top left entry is one, the diagonal entries are $A_1,\dots,A_r$, the remaining entries are zero.

\begin{lem}[Fourier series, LTI state-space equivalence]Suppose there is no state and output uncertainty (the contributions $\mathbf{w}_k\in\mathbb{R}^m,v_k\in\mathbb{R}$ are zero) and the control is zero. The non-linear model in Equation~(\ref{eq:fourier}) can be expressed using the LTI state-space model in Equation~(\ref{eq:state-perf})
\end{lem}
\begin{proof}
  We re-write the Fourier series expression in Equation~(\ref{eq:fourier}) in complex form.

  $e^{ik}=\cos{k}+i\sin{k}$ expresses the well-known Euler's formula, therefore $e^{-ik}=\cos{k}-i\sin{k}$. We find the expression for $\cos{k}=(e^{ik}+e^{-ik})/2$ and $i\sin{k}=(e^{ik}-e^{-ik})/2i$ by substitution of $i\sin{k}$ and $\cos{k}$ respectively. This leads
  \begin{equation}
    h(k)=a_0+\sum_{n=1}^r{e^{ink}(a_n-ib_n)/2},
  \end{equation}
where $i$ is the imaginary unit, and $h(k)\in\mathbb{C}$.

Consider the continuous form of Equation~(\ref{eq:state-perf}), $\dot{\mathbf{q}}=A\mathbf{q}$, with an initial guess $\mathbf{q}_0$. The solution at time $k$ can be expressed $\mathbf{q}=e^{Ak}\mathbf{q}_0$. Both the solution and the system in Equation~(\ref{eq:state-perf}) are well established expression derived using a standard textbook~\cite{kuo1967automatic}.

>>>>

  @inproceedings{seewald2020beyond,
    title={Beyond Traditional Energy Planning: the Weight of Computations in Planetary Exploration}, 
    author={Seewald, Adam},
    booktitle={IROS Workshop on Planetary Exploration Robots: Challenges and Opportunities (PLANROBO20)},
    pages={3},
    year={2020},
    publisher={ETH Zurich, Department of Mechanical and Process Engineering},
    DOI={10.3929/ethz-b-000450120},
    url={https://adamseew.bitbucket.io/short/beyond2020}
  }
  @inproceedings{lindemann2005smoothly,
    title={Smoothly blending vector fields for global robot navigation},
    author={Lindemann, Stephen R and LaValle, Steven M},
    booktitle={Proceedings of the 44th IEEE Conference on Decision and Control},
    pages={3553--3559},
    year={2005},
    organization={IEEE}
  }
  @article{gonccalves2010vector,
    title={Vector fields for robot navigation along time-varying curves in $n$-dimensions},
    author={Gon{\c{c}}alves, Vin{\'\i}cius M and Pimenta, Luciano CA and Maia, Carlos A and Dutra, Bruno CO and Pereira, Guilherme AS},
    journal={IEEE Transactions on Robotics},
    volume={26},
    number={4},
    pages={647--659},
    year={2010},
    publisher={IEEE}
  }
  @inproceedings{panagou2014motion,
    title={Motion planning and collision avoidance using navigation vector fields},
    author={Panagou, Dimitra},
    booktitle={2014 IEEE International Conference on Robotics and Automation (ICRA)},
    pages={2513--2518},
    year={2014},
    organization={IEEE}
  }
  @inproceedings{zhou2014vector,
    title={Vector field following for quadrotors using differential flatness},
    author={Zhou, Dingjiang and Schwager, Mac},
    booktitle={2014 IEEE International Conference on Robotics and Automation (ICRA)},
    pages={6567--6572},
    year={2014},
    organization={IEEE}
  }
  @article{kapitanyuk2017guiding,
    title={A guiding vector-field algorithm for path-following control of nonholonomic mobile robots},
    author={Kapitanyuk, Yuri A and Proskurnikov, Anton V and Cao, Ming},
    journal={IEEE Transactions on Control Systems Technology},
    volume={26},
    number={4},
    pages={1372--1385},
    year={2017},
    publisher={IEEE}
  }
  @book{kuo1967automatic,
    title={Automatic Control Systems},
    author={Kuo, B.C.},
    isbn={9780130549730},
    lccn={67016388},
    series={Electrical engineering series},
    year={1967},
    publisher={Prentice-Hall}
  }
  @article{moler2003nineteen,
    title={Nineteen dubious ways to compute the exponential of a matrix, twenty-five years later},
    author={Moler, Cleve and Van Loan, Charles},
    journal={SIAM review},
    volume={45},
    number={1},
    pages={3--49},
    year={2003},
    publisher={SIAM}
  }
  @book{ogata2002modern,
    title={Modern Control Engineering},
    author={Ogata, K.},
    isbn={9780130432452},
    lccn={2001021683},
    year={2002},
    publisher={Prentice Hall}
  }
\end{filecontents}

@@

Consider a linear time-invariant (LTI) state-space model
\begin{equation}\label{eq:state-perf}\begin{split}
  \mathbf{q}_{k+1}&=A\mathbf{q}_{k}+B\mathbf{u}_{k}+\mathbf{w}_k,\\
  y_k&=C\mathbf{q}_k+v_k,
\end{split}\end{equation}
where $y_k\in\mathbb{R}_{\geq 0}$ is the instantaneous energy consumption. The state $\mathbf{q}$ are the energy coefficients
\begin{equation}\label{eq:state-details}\begin{split}
  \mathbf{q}_k&=\left[\begin{array}{cccccc}
    \alpha_0 & \alpha_1 & \beta_1 & \cdots & \alpha_r & \beta_r
  \end{array}\right]^T,\\
  A&=\left[\begin{array}{cccc}
    1&    &       &  \\
     & A_1&       &  \\
     &    & \ddots&  \\
     &    &       & A_r 
  \end{array}\right],\,A_i=\begin{bmatrix}1 & 1 \\ -i^2/\xi^2 & 1\end{bmatrix},\\
  C&=\left[\begin{array}{cccccc}
    1 & 1 & 0 & \cdots & 1 & 0
  \end{array}\right],
\end{split}\end{equation}
where $\mathbf{q}_k\in\mathbb{R}^m$ given $m=2r+1$, $A\in\mathbb{R}^{m\times m}$ is the state transmission matrix, and $C\in\mathbb{R}^m$ is the output matrix. In matrix $A$, the top left entry is one, the diagonal entries are $A_1,\dots,A_r$, the remaining entries are zero.

\begin{lem}[Fourier series, LTI state-space equivalence]Suppose there is no state and output uncertainty (the contributions $\mathbf{w}_k\in\mathbb{R}^m,v_k\in\mathbb{R}$ are zero) and the control is zero. The non-linear model in Equation~(\ref{eq:fourier}) can be expressed using the LTI state-space model in Equation~(\ref{eq:state-perf})
\end{lem}
\begin{proof}
We re-write the Fourier series expression in Equation~(\ref{eq:fourier}) in complex form using  The well-known Euler's formula $e^{ik}=\cos{k}+i\sin{k}$, therefore $e^{-ik}=\cos{k}-i\sin{k}$~\cite{ogata2002modern}. We find the expression for $\cos{k}=(e^{ik}+e^{-ik})/2$ and $i\sin{k}=(e^{ik}-e^{-ik})/2i$ by substitution of $i\sin{k}$ and $\cos{k}$ respectively. This leads
  \begin{equation}
    h(k)=a_0+\sum_{j=1}^r{e^{ijk}(a_j-ib_j)/2},
  \end{equation}
where $i$ is the imaginary unit, and $h(k)\in\mathbb{C}$.

Let us consider the continuous form of Equation~(\ref{eq:state-perf}), $\dot{\mathbf{q}}=A\mathbf{q}$, with an initial guess $\mathbf{q}_0$. The solution at time $k$ can be expressed $\mathbf{q}=e^{Ak}\mathbf{q}_0$. Both the solution and the system in Equation~(\ref{eq:state-perf}) are well established expressions derived using a standard textbook~\cite{kuo1967automatic}. To solve the matrix exponential $e^{Ak}$ let us consider the an eigenvectors matrix decomposition method~\cite{moler2003nineteen}.

Matrix decomposition methods works on the similarity transformation of the form $A=VDV^{-1}$. The power series definition of $e^{Ak}$ implies $e^{Ak}=Ve^{Dk}V^{-1}$~\cite{moler2003nineteen}. Let us consider the non-singular matrix $V$ whose columns are eigenvectors of $A$; $V:=\begin{bmatrix}v_1 & \dots & v_m\end{bmatrix}$. We can write $Av_j=\lambda_jv_j\,\,\,\forall j=\{1,\dots,m\}$, where $\lambda_j$ is the $j$-th eigenvalue of $A$.

We use the same approach in terms of $\dot{\mathbf{q}}=A\mathbf{q}$. Initial condition can be expressed $\mathbf{q}_0=\sum_{j=1}^m{\gamma_jv_j}$, and the generic solution $\mathbf{q}_k=\sum_{j=0}^m{\gamma_je^{\lambda_jk}v_j}$. The coefficients $\gamma_j$ are obtained solving $V\mathbf{\gamma}=\mathbf{q}_0$.

Let us further consider the continuous version of matrix $A$ in Equation~(\ref{eq:state-details}); $A_c=A-I$, where $I$ is a properly sized- identity matrix. Let us express the output at time instant $k$ of the model in Equation~(\ref{eq:state-perf}) as a linear combination of the state
\begin{equation}
  y_k=\gamma_0e^{\lambda_0k}v_0+\sum_{j=1}^r{\gamma_je^{\lambda_jk}v_j}
\end{equation}
